---
title: "R Notebook"
output: html_notebook
---

# This markdown will be used to compare S-A axis rank to prediction accuracy within each PFN
# We'll do this analysis in fsaverage5, since this downsampled version allows us to run spin tests


# Load in the libraries
```{r}
library(gifti)
library(R.matlab)
library(RNifti)
library(ciftiTools)
ciftiTools.setOption('wb_path', '/Users/askeller/Documents/workbench/')
library(ggplot2)
library(randomcoloR)
library(ggforce)
library(mgcv)
```


# Get PFN hard parcel assignment in fsaverage5 space
# Note: range of values is 1-17 for the right hemisphere but 1-16 for the left hemisphere (network 17 is right lateralized)
```{r}
# Load in gifti files with PFN hard parcel assignment
PFNs_gii_L<-read_gifti('/Users/askeller/Documents/Kellernet_PrelimAnalysis/SpinTests/hardparcel_LH.fsaverage5.label.gii')
PFNs_gii_R<-read_gifti('/Users/askeller/Documents/Kellernet_PrelimAnalysis/SpinTests/hardparcel_RH.fsaverage5.label.gii')

# Extract the list of ranks
PFNs_L <- PFNs_gii_L[["data"]][["labels"]]
PFNs_R <- PFNs_gii_R[["data"]][["labels"]]
```


# Get S-A axis rank by PFN in fsaverage5 space
```{r}
# Load in gifti files with S-A axis ranks in fsaverage5 from Val's github repo
SA_axis_gii_L<-read_gifti('/Users/askeller/Documents/Kellernet_PrelimAnalysis/SpinTests/SensorimotorAssociation_Axis_LH.fsaverage5.func.gii')
SA_axis_gii_R<-read_gifti('/Users/askeller/Documents/Kellernet_PrelimAnalysis/SpinTests/SensorimotorAssociation_Axis_RH.fsaverage5.func.gii')

# Extract the list of ranks
SA_L <- SA_axis_gii_L[["data"]][["normal"]]
SA_R <- SA_axis_gii_R[["data"]][["normal"]]

SArank_byPFN <- vector()

for (i in 1:17) {
SArank_byPFN[i] <- mean(c(SA_L[PFNs_L==i],SA_R[PFNs_R==i]))
}
```


# Load in prediction accuracy by PFN
```{r}
predacc <- read.csv('/Users/askeller/Documents/Kellernet_PrelimAnalysis/SpinTests/pred_acc_by_PFN.csv')
predacc_PC1 <- predacc$PC1
predacc_PC2 <- predacc$PC2
predacc_PC3 <- predacc$PC3
```


# Calculate spearman rank correlation for the actual S-A axis rank by PFN
```{r}
cor.test(predacc_PC1,SArank_byPFN,method="spearman")
cor.test(predacc_PC2,SArank_byPFN,method="spearman")
cor.test(predacc_PC3,SArank_byPFN,method="spearman")

result_PC1<-cor.test(predacc_PC1,SArank_byPFN,method="spearman")
result_PC2<-cor.test(predacc_PC2,SArank_byPFN,method="spearman")
result_PC3<-cor.test(predacc_PC3,SArank_byPFN,method="spearman")
```


# Load in the results of the spin testing (from SpinTests_ABCD.m which calls AAB's package)
```{r}
Spin_Results_Mat = readMat('/Users/askeller/Documents/Kellernet_PrelimAnalysis/SpinTests/GroupAtlasLabel_Perm.mat');
```


# Compute null distribution of spearman rank correlations with spin test results 
```{r}
SArank_byPFN_spins <- matrix(0,17,1000)
for (it in 1:1000) {
  for (net in 1:17) {
    if (net == 17) {
      SArank_byPFN_spins[net,it] <- mean(Spin_Results_Mat$bigrotr[it,PFNs_R==net])
    } else {
    SArank_byPFN_spins[net,it] <- mean(c(Spin_Results_Mat$bigrotl[it,PFNs_L==net],Spin_Results_Mat$bigrotr[it,PFNs_R==net]))
    }
  }
}

null_spearman_PC1 <- matrix(0,1,1000)
null_spearman_PC2 <- matrix(0,1,1000)
null_spearman_PC3 <- matrix(0,1,1000)
for (it2 in 1:1000) {
spcorr1<-cor.test(predacc_PC1,SArank_byPFN_spins[,it2],method="spearman")
null_spearman_PC1[1,it2]<-spcorr1$estimate

spcorr2<-cor.test(predacc_PC2,SArank_byPFN_spins[,it2],method="spearman")
null_spearman_PC2[1,it2]<-spcorr2$estimate

spcorr3<-cor.test(predacc_PC3,SArank_byPFN_spins[,it2],method="spearman")
null_spearman_PC3[1,it2]<-spcorr3$estimate
}

# check null distributions
hist(null_spearman_PC1)
hist(null_spearman_PC2)
hist(null_spearman_PC3)
```





# Plot the results
```{r}
png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC1acc_Spins.png",
    width = 2000, 
    height = 2000,
    res=750)
hist(null_spearman_PC1,xlab="Spearman Correlations",border="lightgray",xlim=c(-1,1))
abline(v=result_PC1$estimate,col="goldenrod",lwd=4)
dev.off()

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC2acc_Spins.png",
    width = 2000, 
    height = 2000,
    res=750)
hist(null_spearman_PC2,xlab="Spearman Correlations",border="lightgray",xlim=c(-1,1))
abline(v=result_PC2$estimate,col="goldenrod",lwd=4)
dev.off()

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC3acc_Spins.png",
    width = 2000, 
    height = 2000,
    res=750)
hist(null_spearman_PC3,xlab="Spearman Correlations",border="lightgray",xlim=c(-1,1))
abline(v=result_PC3$estimate,col="goldenrod",lwd=4)
dev.off()

## Combine data frame and z-score the S-A axis ranks for visualization
df.acc.SA <- cbind.data.frame(predacc_PC1,predacc_PC2,predacc_PC3,SArank_byPFN)
df.acc.SA$SArank_byPFN <- (df.acc.SA$SArank_byPFN - mean(df.acc.SA$SArank_byPFN,na.rm=TRUE))/sd(df.acc.SA$SArank_byPFN,na.rm=TRUE)


png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC1acc.png",
    width = 4000, 
    height = 4000,
    res=1000)
ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC1,color=SArank_byPFN)) + geom_point(size=3) + geom_smooth(method=lm,color='black') + theme_classic() +
  theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 0) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy (General Cognition)")
dev.off()


png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC2acc.png",
    width = 4000, 
    height = 4000,
    res=1000)
ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC2,color=SArank_byPFN)) + geom_point(size=3) + geom_smooth(method=lm,color='black') + theme_classic() +
  theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 0) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy (Executive Function)")
dev.off()

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC3acc.png",
    width = 4000, 
    height = 4000,
    res=1000)
ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC3,color=SArank_byPFN)) + geom_point(size=3) + geom_smooth(method=lm,color='black') + theme_classic() +
  theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 0) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy (Learning/Memory)")
dev.off()


```


# wider format figures for poster 
```{r}
png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC1acc_wide.png",
    width = 3000, 
    height = 2800,
    res=1000)
ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC1,color=SArank_byPFN)) + geom_point(size=3) + geom_smooth(method=lm,color='black') + theme_classic() +
  theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 0) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy")
dev.off()


png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC2acc_wide.png",
    width = 3000, 
    height = 2800,
    res=1000)
ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC2,color=SArank_byPFN)) + geom_point(size=3) + geom_smooth(method=lm,color='black') + theme_classic() +
  theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 0) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy")
dev.off()

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC3acc_wide.png",
    width = 3000, 
    height = 2800,
    res=1000)
ggplot(data=df.acc.SA,aes(SArank_byPFN,predacc_PC3,color=SArank_byPFN)) + geom_point(size=3) + geom_smooth(method=lm,color='black') + theme_classic() +
  theme(legend.position = "none", panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  scale_color_gradient2(high = "#6f1282", mid = "#f9f7fa", low = "goldenrod1", aesthetics = "color", midpoint = 0) + xlab("S-A Axis Rank") + ylab("Prediction Accuracy")
dev.off()



png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC1acc_Spins_wide.png",
    width = 1500, 
    height = 1800,
    res=500)
hist(null_spearman_PC1,xlab="Spearman Correlations",border="lightgray",xlim=c(-1,1))
abline(v=result_PC1$estimate,col="goldenrod",lwd=4)
dev.off()



png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC2acc_Spins_wide.png",
    width = 1500, 
    height = 1800,
    res=500)
hist(null_spearman_PC2,xlab="Spearman Correlations",border="lightgray",xlim=c(-1,1))
abline(v=result_PC2$estimate,col="goldenrod",lwd=4)
dev.off()

png("/Users/askeller/Documents/Writing_InProgress/PFNs_Cognition/SArank_PC3acc_Spins_wide.png",
    width = 1500, 
    height = 1800,
    res=500)
hist(null_spearman_PC3,xlab="Spearman Correlations",border="lightgray",xlim=c(-1,1))
abline(v=result_PC3$estimate,col="goldenrod",lwd=4)
dev.off()
```


